### 2025-04-09 frontmatter/abstract.tex
T-1 day to initial submission, nearly complete draft up to citations and small comments.

\begin{Abstract}
\begin{changemargin}{1cm}{1cm}
This thesis presents the author's work in developing probes of the inner structure of jets in high-energy particle collisions.
%
We begin by introducing QCD and the scattering of partons (quarks and gluons), discussing jets as theoretical and experimental proxies for partonic physics, and presenting the partonic cascade model of jet formation and jet substructure.
%
Noting the ubiquitous presence of low-energy pollution in particle collision events, in the forms of hadronization, detector effects, the underlying event (UE), and pileup (PU), we then move towards the modern research area of developing pollution-insensitive probes of the jet substructure.
%
Pollution-insensitive features of jet substructure are usually accessed either through jet grooming or energy-weighted correlation functions.
%
We present the basics of the modern theory of jet grooming as well as the work of the author in developing the \textsc{Piranha} paradigm for \textit{continuous} jet grooming, introduced by the author in \Reff{}, and explore the formal and phenomenological benefits of continuous grooming techniques as pollution-insensitive probes of jet substructure.
%
We also introduce the basics of the simplest energy-weighted correlation function -- the energy-energy correlator (EEC), which probes angular correlations between particle pairs -- and discuss the efficient and intuitive higher-point analogues introduced by the author in \Reff{}, which provide computationally-realistic, pollution-insensitive probes of angular many-body correlations in QCD jets.
%
Finally, we exposit the generic theory of energy-weighted observable correlations (EWOCs), introduced by the author in \Reff{}, which utilize the energy weighting of the EEC to provide pollution-insensitive probes of non-angular correlations within jets.
\end{changemargin}
\end{Abstract}

>>>>

\begin{Abstract}
\begin{changemargin}{0.5cm}{0.5cm}
This thesis presents the author's work in developing probes of the inner structure of jets in high-energy particle collisions.
%
We begin by introducing QCD and the scattering of partons (quarks and gluons), discussing jets as theoretical and experimental proxies for partonic physics, and presenting the partonic cascade model of jet formation and jet substructure.
%
Noting the ubiquitous presence of low-energy pollution in particle collision events, in the forms of hadronization, detector effects, the underlying event (UE), and pileup (PU), we then move towards the modern research area of developing pollution-insensitive probes of the jet substructure.
%
Pollution-insensitive features of jet substructure are usually accessed either through jet grooming or energy-weighted correlation functions.
%
We present the basics of the modern theory of jet grooming as well as the work of the author in developing the \textsc{Piranha} paradigm for \textit{continuous} jet grooming, introduced by the author in \Reff{Alipour-Fard:2023prj}, and explore the formal and phenomenological benefits of continuous grooming techniques as pollution-insensitive probes of jet substructure.
%
We also introduce the basics of the simplest energy-weighted correlation function -- the energy-energy correlator (EEC), which probes angular correlations between particle pairs -- and discuss the efficient and intuitive higher-point analogues introduced by the author in \Reff{Alipour-fard:2024szj}, which provide computationally-realistic, pollution-insensitive probes of angular many-body correlations in QCD jets.
%
Finally, we exposit the generic theory of energy-weighted observable correlations (EWOCs), introduced by the author in \Reff{Alipour-fard:2025dvp}, which utilize the energy weighting of the EEC to provide pollution-insensitive probes of non-angular correlations within jets.
\end{changemargin}
\end{Abstract}

### 2025-04-09 frontmatter/acknowledgements.tex
T-1 day to initial submission, nearly complete draft up to citations and small comments.

%\epigraph{``Understanding is love's other name.''}{Thich Nhat Hanh}
%%
%\epigraph{``We're philosophers. We think, therefore we am.''}{\textit{Small Gods}, Terry Pratchett}
% \epigraph{Films live or die on their casting.}{\href{https://youtu.be/W5bB7-jg_4M?list=PLomTW5B3fAMXJsqE_HDiMpdOdcfAk_Lqc&t=146}{Peter Jackson}}

My first acknowledgements are to my tireless advisor, Jesse Thaler.
%%
%Jesse, you were there with me and for me at MIT from the beginning.
%%
%I remember the email in which you invited me to MIT, our first couple of meetings where we had several wonderful conversations about physics, and your steadfast assurance that I am an important and welcome member of your group.
%
Thank you for taking me under your vast wing.

Rikab Gambhir
%
Sean Benevedes

My second acknowledgments are to my parents, without whom I would surely not be here.

Tengiz Bibilashvili
%
Seth Koren
%
Nathaniel Craig
%
Wouter Waalejwin

Liam Bradley
%
Noah Mihelic
%
Daniel Kreizberg
%
Nate Gardner
%
Kyreija Lamothe
%
Vince Fleming
%
Ryan Croy
%
Rose
%
Erin Neitzel
%
Jason Georgis
%
Johannes Klein
%
Nicholas Maguid

David Rower
(his parents, Nathan Rower)
%
Nick O'Dea
%
James Ehrets
(his parents)
%
David Newsom
%
Jasmin Kwak
%
Ben Siegel
%
Dolev Bluvstein
%
J Rogers

Yurim Lee
%
Kai Goh
%
Eugene Ma
%
Brandon Louie
%
other breakers?
%
Alvin Ong
%
Anoop Praturu
%
Ryan Stuart
%
Marvin Qi

Dimitra Pefkou
%
Jamison Sloan
%
Asmund Folkestad
%
Sarah Geller
%
Yitian Sun
%
Gregory Ridgeway
%
Robert Jones

Neeraj Tata
%
Lamia Ateshian
%
Sarah
%
George
%
Miguel
%
Nathan Everett and Lubah
%
Adam Platek
%
Zhiquan Sun, who taught me that a happy life means eating well.
%
Patrick Oare, Wenzer Qin, Artur Avkadiev
%
Nick Kamp, Caolan John
%
Ouail Kitouni
%
Marianne Moore, Anjie Gao, Manu Srivasta
%
Joshua Lin
%
Atakan Firat, who never backs down from a fight.
%
Lisa Yang, whose constant drive for self-improvement is always inspiring

Jasper Pont, who I still miss.

>>>>

\epigraph{``Understanding is love's other name.''}{Thich Nhat Hanh}
\vspace{-20pt}
\epigraph{``We're philosophers. We think, therefore we am.''}{\textit{Small Gods}, Terry Pratchett}
\vspace{-20pt}
\epigraph{Films live or die on their casting.}{\href{https://youtu.be/W5bB7-jg_4M?list=PLomTW5B3fAMXJsqE_HDiMpdOdcfAk_Lqc&t=146}{Peter Jackson}}

I try as often as I can to remember that we live on a miraculous, miniscule blue dot floating in a vast expanse of emptiness, with scant resources and an incredible story.
%
It is the joy of my life to be part of the humanity sector of team earth.

\vspace{10pt}
\hrule

\begin{center}
Like most of the humanity sector, I am nothing without my mentors.
\end{center}

My first acknowledgements are to my tireless advisor, Jesse Thaler.
%
Thank you for taking me under your vast wing.
%
I have been very lucky to learn from your mastery over every aspect of the scientific process.
%
I have never seen someone do and change so much in the world in such a short time.

My second acknowledgments are to my parents, without whom I would surely not be here.
%
My mother taught me, through her shining example, the values of kindness, openness, acceptance, and sharp awareness and fighting spirit.
%
My father taught me by lack of example the importance of \glslink{jet-grooming}{grooming}, discussed further in \Chap{grooming}.
%
He also gave me the gifts of critical thinking, his jeans, and uncountable priceless lessons, experiences, and memories.

Tengiz Bibilashvili, my academic advisor during my time as an undergraduate at the University of California, Santa Barbara (UCSB), is one of the sharpest, kindest, brightest, and most generous human beings I have ever met.
%
I am grateful every day that I was lucky enough to experience his teaching.

Nathaniel Craig, my research advisor at UCSB, is a powerhouse of intellect, creativity, and pedagogy;
%
I benefited deeply from his dedication to mentorship and patience, and would have been lost on the tip of the iceberg of quantum field theory without his guidance (though, as he would always say with a smile, he was ``just doing his job'').

There is not enough I can say about the mentorship of Seth Koren.
%
Seth is incredibly empathetic and creative, and a brilliant teacher.
%
Seth is, to me, a quintessential human being:
%
a philosopher, clever and kind, who accepts nothing but the truth.

Finally, Wouter Waalejwin, who I met in the fourth year of my PhD, has been an incredibly patient mentor and a valuable resource for me in learning the ins and outs of quantum chromodynamics.
%
His presence is felt in many subtle ways throughout this thesis.
%
I can see his gentle, knowing smile even now.

I would also like to thank Iain Stewart and Christoph Paus.
%
They are members of my thesis committee, and I am grateful for their time and effort on my behalf, but I am most grateful for the environment they created at MIT through their presence.
%
They always had a kind smile to wear, a warm comment to make, or a laugh to share.
%
I knew I could always go to Iain with any question or concern and receive a listening ear and some sound advice.
%
I knew that I could always share a joke and a lighthearted chuckle with Christoph.

On the topic of environment, I would finally like to thank Daniel Harlow.
%
\sam{}

\vspace{12pt}
\hrule
\vspace{12pt}

My sisters, Christina Nazmi-Williams and Mehrnoush Minor (\textit{in alphabetical order}), are my role models and favorite people.
%
It is thanks to their hard work and sacrifices on my behalf that I have been able to live such a clear and irresponsible life.
%
I am so lucky to be in their family.
%
Thomas Minor, my brother-in-law, is another favorite.
%
I aspire to someday be like Tom:
%
brilliant and humble, quietly aware and listening more than speaking, kind and gentle with a troublemaking streak.
%
My nephews and niece -- Ethan and Mason Williams, and Alex and Amelia Minor -- are bundles of joy and diamonds of my life.

My godparents
%
My godsister
%
Last but not least, my godbrother

I also have the best siblings I could ever hope not to be related to.
%
Noah Mihelic (with credit and gratitude to my adopted family: ), who I knew before I had memories, has given me clarity, critical reasoning, incredible companionship, and many magical adventures.
%
David Rower (with credit and gratitude to my adopted family: Rachel Goldberg, Tobin Rower, Nathan Rower, and Lamia Ateshian)
%
J Rogers
%
Neeraj Tata

Sean Benevedes
%
Rikab Gambhir

\vspace{10pt}
\hrule
\vspace{10pt}

The remainder of my acknowledgments are mostly chronological, and no less heartfelt.

Liam Bradley
%
Daniel Kreizberg
%
Nate Gardner
%
Kyreija Lamothe
%
Vince Fleming
%
Ryan Croy
%
Rose
%
Erin Neitzel
%
Jason Georgis
%
Johannes Klein
%
Nicholas Maguid
%
Nathan Everett and Lubah

James Ehrets
(his parents)
%
Nick O'Dea
%
David Newsom
%
Jasmin Kwak
%
Ben Siegel
%
Dolev Bluvstein
%
Anoop Praturu
%
Ryan Stuart
%
Marvin Qi
%
Kai Goh
%
Eugene Ma
%
Brandon Louie
%
other breakers?
%
Alvin Ong
%
Yurim Lee

Zhiquan Sun, who taught me that a happy life means eating well.
%
Shankar Balasubramanian
%
Margarita Davydova
%
Atakan Firat, who never backs down from a fight.
%
Anjie Gao, who taught me (among other things) the wisdom that ``nothing is trivial''.
%
Patrick Oare, Wenzer Qin, Artur Avkadiev
%
Nick Kamp, Caolan John
%
Ouail Kitouni

Dimitra Pefkou
%
Asmund Folkestad
%
Yitian Sun
%
Gregory Ridgeway
%
Jamison Sloan
%
Sarah Geller
%
Robert Jones
%
Anita Budhraja

Lisa Yang, whose constant drive for self-improvement is always inspiring
%
Marianne Moore, Manu Srivasta
%
Joshua Lin
%
Sarah M
%
George
%
Miguel

Jasper Pont, whose free a

\vspace{12pt}
\hrule

\begin{center}
    \textit{Ashes to ashes, dust to dust.}
\end{center}

### 2025-04-09 frontmatter/notation.tex
T-1 day to initial submission, nearly complete draft up to citations and small comments.

% =====================================
\begin{sambox}{Resources}{}
    % ---------------------------------
    \begin{itemize}
        \item
            Larkoski Chapter 9:
            %
            ee to hadrons, jets, splitting functions, pheno problems

        \item
            Foundations Chapter 8:
            %
            Factorization, Mellin, DGLAP, sum rules

        \item
            Substructure Chapter 1:
            %
            Substructure motivation
    \end{itemize}
    % ---------------------------------
\end{sambox}
% =====================================

@@

        \item
            List of problems

        \item
            Signature page

@@

Here is some common notation used throughout this thesis.
%
See \Sec{morenotation} for a more comprehensive list.

\begin{itemize}
    \item
        A \vocab{calcule} is a smaller analogue of a calculation (such as a simple example or a part of a bigger calculation)

    \item
        \(A := B\) means ``\(A\) is defined to mean \(B\)'', as does \(B =: A\);

@@

    \item
        \sam{Metric signature}

    \item
        The Mellin transform of a function \(f(x)\) on the interval $(0,\infty)$ is defined as
        \begin{align}
            \mathcal{M}[f](s)
            \eqdelta
            \int_0^\infty \,\frac{\dd x}{x}\, x^{s-1} \, f(x)
            \eqdelta
            \hat f(s)
            .
        \end{align}

        For all of the applications in this work, other than some derivations which are relegated to the Problems \sam{of Chapter...}, the functions in whose Mellin transforms we are interested will have support only on the interval \((0,1)\).
        %
        Therefore, unless stated otherwise, the Mellin transform appearing in this work will appear in the form
        \begin{align}
            \hat f(s)
            \eqdelta
            \int_0^1 \,\frac{\dd x}{x}\, x^{s-1} \, f(x)
            .
        \end{align}

        \sam{Put into the text where relevant}

        \sam{Mention here the part of the text where this appears and the problems in which it appears}

@@

    \item
        The \textit{energy fraction} carried by a particular particle in a scattering event or jet, relative to the total energy of the event or jet, will play an important role in this thesis.
        %
        We will use the symbol \(z_i\) to denote the energy fraction particle \(i\) within a jet or event:
        \begin{align}
            z_i
            \eqdelta
            \frac{E_i}{E_\text{tot}}
            .
        \end{align}
        \sam{Revisit}

    \item
        We will also use the following standard definitions:
        \begin{subequations}
        \label{eq:qcd_coupling}
        \begin{align}
            \label{eq:as_defn}
            \as &= \frac{\alpha_s}{4\pi}
            \\
            \label{eq:beta_fn_defn}
            \frac{\dd}{\dd\log\mu}\alpha_s(\mu)
            &\eqdelta
            \beta(\alpha_s)
            =
            -2\beta_0 \alpha_s(\mu)^2 + \mathcal{O}\le(\alpha_s(\mu)^3\ri)
            \\
            \label{eq:alphas_1loop}
            \alpha_s^\text{(1-loop)}(\mu)
            &=
            \frac{\alpha_s(Q)}{1 + 2\alpha_s(Q) \beta_0 \log(\frac{\mu}{Q})}
            ,
        \end{align}
        where
        \begin{align}
            \beta_0 = \frac{1}{12\pi}\le(11\,C_A - 4\,T_f n_f\ri)
        \end{align}
        \end{subequations}
        is the leading coefficient of the QCD beta function, \(n_f = 5\) denotes the number of effectively massless quark flavors, \(Q\) indicates a reference scale (such as the energy scale of a hard process), and
        \begin{subequations}
        \label{eq:group_theory}
        \begin{align}
            C_F &= \frac{N_c^2 - 1}{2N_c}
            % \xrightarrow[]{\text{QCD}}
            % \frac{4}{3}
            \\
            C_A &= N_c
            % \xrightarrow[]{\text{QCD}}
            % 3
            \\
            T_F &= \frac{1}{2}
            ,
        \end{align}
        \end{subequations}
        denote the quadratic Casimir for the fundamental representation of \(SU(N_c)\), the quadratic Casimir for the adjoint representation, and the Dynkin index of the fundamental representation, respectively.
        %
        The expressions of \Eq{group_theory} are often referred to collectively as \textit{group theory factors}.
        %
        For QCD, \(N_c = 3\), \(C_F = 4/3\), and \(C_A = 3\), giving \(
            \beta_0 = \le(11 - 2 n_f / 3\ri)/4\pi
            .
        \)

%         A useful definition for clarity is that of the value of \(\alpha_s\) divided by \(4\pi\), since this quantity appears in loop computations (which often have a \(4\pi\) suppression):
%         \begin{subequations}
%         \begin{align}
%             a_s = \frac{\alpha_s}{4\pi}
%         \end{align}
%         \end{subequations}
\end{itemize}

Furthermore, we will assume
\begin{itemize}
    \item
    That all partons other than the top quark are massless;

>>>>

@@

@@

Here is some common notation used throughout this thesis.

\begin{itemize}
    \item
        \(A := B\) means ``\(A\) is defined to mean \(B\)'', as does \(B =: A\);

@@

    \item
        We make the unfortunate choice to use the ``mostly-minus'' metric, \(g^{\mu\nu} = \text{diag}\le(+,\,-,\,-,\,-\ri)\), with the gamma matrix algebra \(\acomm{\gamma^\mu}{\gamma^\nu} = 2 g^{\mu\nu}\,.\).

    \item
        The Mellin transform of a function \(f(x)\) with support on the interval \((0,1)\) (as in all concrete applications in this work) is
        \begin{align}
            \mathcal{M}[f](s)
            \eqdelta
            \int_0^1 \,\frac{\dd x}{x}\, x^{s-1} \, f(x)
            =
            \hat f(s)
            \,.
        \end{align}

@@

    \item
        The \textit{energy fraction} carried by a particular particle in a scattering event or jet, relative to the total energy of the event or jet, will play an important role in this thesis.
        %
        We will use the symbol \(z_i\) to denote the energy fraction particle \(i\) relative to a ``parent'' of any type, such as a pair of particles, a jet, or an entire event (which of these should be clear based on context):
        \begin{align}
            z_i
            \eqdelta
            \frac{E_i}{E_\text{tot}}
            \,.
        \end{align}

    \item
        We will also use the following standard definitions:
        \begin{subequations}
        \label{eq:qcd_coupling}
        \begin{align}
            \label{eq:as_defn}
            \as &= \frac{\alpha_s}{4\pi}
            \\
            \label{eq:beta_fn_defn}
            \frac{\dd}{\dd\log\mu}\alpha_s(\mu)
            &\eqdelta
            \beta(\alpha_s)
            =
            -2\beta_0 \alpha_s(\mu)^2 + \mathcal{O}\le(\alpha_s(\mu)^3\ri)
            \\
            \label{eq:alphas_1loop}
            \alpha_s^\text{(1-loop)}(\mu)
            &=
            \frac{\alpha_s(Q)}{1 + 2\alpha_s(Q) \beta_0 \log(\frac{\mu}{Q})}
            ,
        \end{align}
        where
        \begin{align}
            \beta_0 = \frac{1}{12\pi}\le(11\,C_A - 4\,T_f n_f\ri)
        \end{align}
        \end{subequations}
        is the leading coefficient of the QCD beta function, \(n_f = 5\) denotes the number of effectively massless quark flavors, \(Q\) indicates a reference scale (such as the energy scale of a hard process), and
        \begin{subequations}
        \label{eq:group_theory}
        \begin{align}
            C_F &= \frac{N_c^2 - 1}{2N_c}
            \xrightarrow[]{\text{QCD}}
            \frac{4}{3}
            \\
            C_A &= N_c
            \xrightarrow[]{\text{QCD}}
            3
            \\
            T_F &= \frac{1}{2}
            ,
        \end{align}
        \end{subequations}
        denote the quadratic Casimir for the fundamental representation of \(SU(N_c)\), the quadratic Casimir for the adjoint representation, and the Dynkin index of the fundamental representation, respectively.
        %
        The expressions of \Eq{group_theory} are often referred to collectively as \textit{group theory factors}.
        %
        For QCD, \(N_c = 3\), \(C_F = 4/3\), and \(C_A = 3\), giving \(
            \beta_0 = \le(11 - 2 n_f / 3\ri)/4\pi
            .
        \)
\end{itemize}

Furthermore, we will assume
\begin{itemize}
    \item
    That all partons are massless other than the top quark (whose effects we will mostly ignore);

### 2025-04-09 includes/glossary.tex
T-1 day to initial submission, nearly complete draft up to citations and small comments.

% DEBUG? Not showing up correctly, but may not want to include anyway
\newglossaryentry{beta-sd}
{
    name=\ensuremath{\beta_\text{SD}},
    description={
        A parameter controlling the angular dependence of the \glsxshort{sd} algorithm.
        %
        As \(beta_\text{SD}\) gets larger, SD is more and more biased to remove wide-angle radiation;
    }
}

@@

% DEBUG? Not showing up correctly, but may not want to include anyway
%\newglossaryentry{fsoft}
%{
%    name=\ensuremath{f_{\text{soft}}},
%    description={%
%        The fraction of the jet energy that is removed by \glsxshort{rsf}.
%        %
%        % The \gls{rsf} algorithm is described in \Section~\ref{sec:rsf}.
%    }
%}

@@

\newglossaryentry{confinement}
{
    name=confinement,
    description={
    }
}

@@

\newglossaryentry{dglap}
{
    name=Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP),
    description={
        Physicists who contributed deeply to the foundational results of perturbative QCD that bear their names.
    }
}

@@

\newglossaryentry{discontinuity}
{
    name=discontinuity,
    description={
        Also see continuity
    }
}
    \newglossaryentry{clustering-discontinuity}
    {
        name=of jet clustering,
        description={Angular-discontinuous behavior of jet clustering algorithms due to their clustering criteria},
        parent=discontinuity,
    }

    \newglossaryentry{soft-discontinuity}
    {
        name=soft,
        text=soft discontinuity,
        description={A discontinuity sensitive to the emission of small amounts of energy},
        parent=discontinuity,
    }

    \newglossaryentry{angular-discontinuity}
    {
        name=angular,
        description={A discontinuity sensitive to small angular variations in energy flow},
        parent=discontinuity,
    }

@@

    \newglossaryentry{soft-drop}
    {
        % type=\acronymtype,
        name=Soft Drop (SD),
        % name=SD,
        description={a two-parameter family of discontinuous jet groomers},
        first={the Soft Drop de-clustering algorithm (Soft Drop, or SD)},
        text={Soft Drop},
        short={SD},
        long={Soft Drop de-Clustering algorithm},
        parent=jet-grooming
    }

@@

\newglossaryentry{phd}
{
  name=parton-hadron duality (PHD),
  description={
      A principle of pQCD in which the parton-level predictions of energy-flow are assumed to be similar to the energy-flow at hadron-level.
      %
      Not to be confused with PhD \sam{fill out}
  },
}

    \newglossaryentry{lphd}
    {
      name=local parton-hadron duality (LPHD),
      description={A refinement of the principle of PHD in which \sam{}.
      %
      See preconfinement},
      parent=phd
    }

@@

\newglossaryentry{partonshower}
{
  name=parton shower,
  text=parton shower,
  description={See also tree of partonic splittings}
}

@@

@@

\newglossaryentry{softsing}
{
  name=soft singularity,
  first=\vocab{soft singularity},
  description={}
}

@@

\newglossaryentry{track}
{
  name=track,
  description={}
}

    \newglossaryentry{trackfn}
    {
      name=function,
      text=track function,
      description={},
      parent=track
    }

>>>>

%\newglossaryentry{beta-sd}
%{
%    name=\ensuremath{\beta_\text{SD}},
%    description={
%        A parameter controlling the angular dependence of the \glsxshort{sd} algorithm.
%        %
%        As \(beta_\text{SD}\) gets larger, SD is more and more biased to remove wide-angle radiation;
%    }
%}

@@

%\newglossaryentry{fsoft}
%{
%    name=\ensuremath{f_{\text{soft}}},
%    description={%
%        The fraction of the jet energy that is removed by \glsxshort{rsf}.
%        %
%        % The \gls{rsf} algorithm is described in \Section~\ref{sec:rsf}.
%    }
%}

@@

\newglossaryentry{confinement}
{
    name=confinement,
    description={
        The phenomenon of QCD where quarks and gluons are permanently bound within composite hadrons, and cannot be isolated as free particles
    }
}

@@

\newglossaryentry{dglap}
{
    name=Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP),
    description={
        Physicists who contributed deeply to foundational results of perturbative QCD, including those that bear their names.
    }
}

@@

\newglossaryentry{discontinuity}
{
    name=discontinuity,
    description={
        Also see continuity
    }
}
    \newglossaryentry{clustering-discontinuity}
    {
        name=of jet clustering,
        text={clustering discontinuity},
        plural={clustering discontinuities},
        description={Angular-discontinuous behavior of jet clustering algorithms due to their clustering criteria},
        parent=discontinuity,
    }

    \newglossaryentry{soft-discontinuity}
    {
        name=soft,
        text=soft discontinuity,
        plural=soft discontinuities,
        description={A discontinuity sensitive to the emission of small amounts of energy},
        parent=discontinuity,
    }

    \newglossaryentry{angular-discontinuity}
    {
        name=angular,
        text={angular discontinuity},
        plural={angular discontinuities},
        description={A discontinuity sensitive to small angular variations in energy flow},
        parent=discontinuity,
    }

@@

    \newglossaryentry{soft-drop}
    {
        % type=\acronymtype,
        name=Soft Drop (SD),
        % name=SD,
        description={a two-parameter family of hard-cutoff jet groomers},
        first={the Soft Drop de-clustering algorithm (Soft Drop, or SD)},
        text={Soft Drop},
        short={SD},
        long={Soft Drop de-Clustering algorithm},
        parent=jet-grooming
    }

@@

\newglossaryentry{phd}
{
  name=parton-hadron duality (PHD),
  first=parton-hadron duality (PHD),
  text=PHD,
  description={
      A principle of pQCD in which the parton-level predictions of energy-flow are assumed to be similar to the energy-flow at hadron-level.
      %
      Not to be confused with PhD \sam{fill out}
  },
}

    \newglossaryentry{lphd}
    {
      name=local parton-hadron duality (LPHD),
      first=local parton-hadron duality (LPHD),
      text=LPHD,
      description={A refinement of the principle of PHD in which \sam{}.
      %
      See preconfinement},
      parent=phd
    }

@@

\newglossaryentry{partonshower}
{
  name=parton shower,
  text=parton shower,
  description={Any probabilistic algorithm that applies the principles of partonic cascade to produce final-state particles given an initial set of particles}
}

@@

\newglossaryentry{soft-limit}
{
    name=soft limit,
    description={
        A limit in which a single particle in a scattering process has very small energy, with universal features described by soft theorems (e.g. soft photon or gluon theorems)
    }
}

@@

@@
